% BpfReJIT: Safe Post-Load JIT Specialization for Kernel eBPF
% ACM SIGCONF format, anonymous submission

\documentclass[sigconf,anonymous]{acmart}

\usepackage{microtype}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{url}
\usepackage{subcaption}
\usepackage{array}
\usepackage{tabularx}

% ACM copyright / DOI setup (for submission, leave as default)
\setcopyright{acmlicensed}
\copyrightyear{2026}
\acmYear{2026}
\acmDOI{XXXXXXX.XXXXXXX}
\acmConference[OSDI '26]{20th USENIX Symposium on Operating Systems Design and Implementation}{July 2026}{Santa Clara, CA, USA}
\acmBooktitle{20th USENIX Symposium on Operating Systems Design and Implementation (OSDI '26), July 2026, Santa Clara, CA, USA}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/26/07}

% Code listing style
\lstset{
  basicstyle=\ttfamily\footnotesize,
  keywordstyle=\color{blue}\bfseries,
  commentstyle=\color{gray},
  stringstyle=\color{orange},
  breaklines=true,
  numbers=left,
  numberstyle=\tiny\color{gray},
  frame=single,
  xleftmargin=1em,
  xrightmargin=0.5em,
}

% Compact table spacing
\setlength{\tabcolsep}{4pt}

\begin{document}

\title{BpfReJIT: Safe Post-Load JIT Specialization\\for Kernel eBPF}

\author{Anonymous Authors}
\affiliation{\institution{Anonymous Institution}}
\email{anonymous@example.com}

\begin{abstract}
eBPF is widely deployed for network policy, load balancing,
observability, and scheduling.  The kernel JIT-compiles each program
into native machine code that runs in kernel context---where a
code-generation bug can crash the machine.  The JIT is therefore conservative: each BPF instruction maps to a
fixed native sequence, and every instruction selection decision is
hardcoded.  Operators cannot
influence these choices, though the right ones depend on workload,
microarchitecture, and deployment context the kernel lacks.

Adding smarter heuristics to the kernel does not help: the same
optimization can improve one workload and degrade another, and
heuristics that are individually beneficial interact badly when
combined.  Nor can operators supply native code directly---the kernel
must be the sole source of the instructions it runs.

We present \textsc{BpfReJIT}, which decouples \emph{safety} from
\emph{optimization} in the kernel JIT\@.  The kernel determines which
native code variants are safe to emit; privileged userspace selects
which to apply for each program, based on workload and deployment
context.  Evaluation shows that selective re-compilation captures
available performance gains while avoiding the regressions that fixed
heuristics produce.
\end{abstract}

\begin{CCSXML}
<ccs2012>
  <concept>
    <concept_id>10011007.10011006.10011008.10011009.10011015</concept_id>
    <concept_desc>Software and its engineering~Compilers</concept_desc>
    <concept_significance>500</concept_significance>
  </concept>
  <concept>
    <concept_id>10011007.10011074.10011099.10011102.10011103</concept_id>
    <concept_desc>Software and its engineering~Software performance</concept_desc>
    <concept_significance>300</concept_significance>
  </concept>
  <concept>
    <concept_id>10010520.10010553.10010562</concept_id>
    <concept_desc>Computer systems organization~Operating systems</concept_desc>
    <concept_significance>300</concept_significance>
  </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Compilers}
\ccsdesc[300]{Software and its engineering~Software performance}
\ccsdesc[300]{Computer systems organization~Operating systems}

\keywords{eBPF, JIT compilation, kernel optimization, post-load specialization, mechanism/policy separation}

\maketitle

%% ============================================================
\section{Introduction}
\label{sec:intro}
%% ============================================================

eBPF programs enforce network policy~\cite{cilium}, drive load
balancers~\cite{katran}, power observability, and implement
schedulers~\cite{sched_ext}.  They run on performance-critical code
paths in production infrastructure, and every one of them is
JIT-compiled by the kernel into native machine code that executes in
kernel context.  A code-generation error here can crash the machine.
To prevent this, the kernel JIT maps each BPF opcode to a single
fixed native sequence, with every instruction selection decision
hardcoded and no operator input~\cite{linux_bpf_jit}.

This design conflates two concerns that ought to be separate.  The
kernel must ensure that the generated code is \emph{safe}---this is
non-negotiable.  But the kernel also makes every instruction selection
decision, with no knowledge of the workload, the target
microarchitecture's performance characteristics, or the operator's
deployment constraints.  The result is a measurable code quality gap:
the kernel JIT misses native instruction selection
opportunities---conditional moves, wide-load fusion, rotate
idioms---that the BPF instruction set cannot express and that no
bytecode optimizer~\cite{k2,merlin,epso} can introduce
(\S\ref{sec:motivation}).

The natural response is to add smarter heuristics to the kernel
compiler.  We show this approach is fundamentally limited.  Backend
optimization choices are workload-dependent: the same transformation
improves one program and degrades another, depending on branch
predictability and input distributions.  Individually beneficial
heuristics interact unpredictably when combined, producing regressions
that none causes in isolation.  No fixed policy is correct across
programs (\S\ref{sec:policy_sensitivity}).

Operators need a way to make these choices themselves.  But eBPF's
security model requires the kernel to be the sole generator of the
native code it executes.  Allowing userspace to supply machine code is
unacceptable.

Our insight is that these requirements are not in conflict.
Whether a native instruction alternative is \emph{safe} depends on
the program structure and the CPU---the kernel can determine this.
Whether it is \emph{beneficial} depends on the workload and the
deployment---the operator should decide this.  Separating these two
concerns lets the kernel retain full control over safety while giving
operators control over performance.

We present \textsc{BpfReJIT}, an OS interface built on this
separation.  The kernel defines a bounded set of safe native code
alternatives for recognized instruction patterns; privileged userspace
selects from these alternatives per program and per site, guided by
profiling and deployment policy.  The safety side of the interface is
small and stable across kernel versions; the optimization side evolves
independently, without kernel upgrades.

\textbf{Contributions.}
\begin{itemize}
  \item A characterization of the kernel JIT code quality gap, tracing
    it to native instruction selection deficiencies that bytecode
    optimizers cannot reach (\S\ref{sec:motivation}).
  \item Evidence that fixed kernel heuristics are insufficient:
    workload-dependent optimizations and composition effects produce
    regressions that no individual optimization causes
    (\S\ref{sec:policy_sensitivity}, \S\ref{sec:eval_fixed}).
  \item \textsc{BpfReJIT}: a kernel/userspace interface that decouples
    safety from optimization in the JIT, covering four optimization
    families with a declarative extension mechanism
    (\S\ref{sec:design}, \S\ref{sec:implementation}).
  \item Evaluation on production programs showing that selective
    re-compilation recovers available gains while avoiding every
    regression that fixed heuristics produce
    (\S\ref{sec:evaluation}).
\end{itemize}

%% ============================================================
\section{Background and Motivation}
\label{sec:motivation}
%% ============================================================

\subsection{The eBPF Compilation Pipeline}

An eBPF program goes through three kernel stages: verification (memory
safety, termination), JIT compilation, and execution.  The JIT-compiled
native code runs directly in kernel context, so a code-generation bug
can crash or compromise the kernel.  To keep this safe, the JIT maps
each BPF opcode to a single hand-audited native
sequence~\cite{linux_bpf_jit}---no intermediate representation, no
instruction selection, no peephole optimizer.

The price of this simplicity is that safety and optimization are
inseparable.  The same fixed mapping that guarantees correctness also
locks in every code-generation decision.  Three consequences follow:
(1)~multi-byte values decomposed by the verifier into byte loads are
reconstructed with shift-or chains instead of single wide loads;
(2)~every BPF conditional jump becomes an x86 \texttt{jcc}---there is no
analysis to identify select patterns amenable to \texttt{cmov};
(3)~callee-saved registers are unconditionally saved regardless of usage
(partially addressed in kernel 7.0-rc2 via \texttt{detect\_reg\_usage()}).

\subsection{Why Bytecode Optimizers Cannot Help}

K2~\cite{k2}, Merlin~\cite{merlin}, and EPSO~\cite{epso} optimize BPF
\emph{bytecode}---the input to the JIT, not its output.  Merlin lifts
BPF to LLVM IR where \texttt{select} exists, but must lower back to BPF
bytecode before the kernel JIT runs; the BPF ISA has no \texttt{select}
opcode.  The kernel JIT translates BPF opcodes 1:1; no bytecode rewrite
can introduce an x86 \texttt{cmov}, fuse shifts into a \texttt{lea}, or
replace byte-load chains with a wide \texttt{mov}.  These are native
instruction selection decisions absent from the BPF ISA
(Table~\ref{tab:existing_work}).

\begin{table}[t]
  \centering
  \caption{Comparison with BPF optimization systems.}
  \label{tab:existing_work}
  \small
  \begin{tabular}{lcccc}
    \toprule
    System & Layer & Backend? & Post-load? & Selective? \\
    \midrule
    K2~\cite{k2}          & BPF bytecode & No  & No  & No  \\
    Merlin~\cite{merlin}  & LLVM IR+BPF  & No  & No  & No  \\
    EPSO~\cite{epso}      & BPF bytecode & No  & No  & No  \\
    \textbf{BpfReJIT}     & \textbf{JIT backend} & \textbf{Yes} & \textbf{Yes} & \textbf{Yes} \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Quantifying the Code Quality Gap}
\label{sec:characterization}

\textbf{Methodology.} We compare the kernel JIT (Linux 6.15.11) against
llvmbpf on 31 pure-JIT microbenchmarks that isolate code generation
quality (no map lookups on the hot path). Each benchmark runs 30
iterations of 1{,}000 repeats; we report the per-benchmark median of
per-iteration medians. We use paired Wilcoxon signed-rank tests with
Benjamini-Hochberg correction and bootstrap 95\% CIs for suite-level
geomeans. Platform: Intel Core Ultra 9 285K (Arrow Lake-S), performance
governor, turbo disabled.

\begin{table}[t]
  \centering
  \caption{Kernel JIT code quality gap: suite-level summary.}
  \label{tab:exec_summary}
  \begin{tabular}{lrrr}
    \toprule
    Suite & Geomean (L/K) & 95\% CI & Sig.\ / Total \\
    \midrule
    Pure-JIT (31) & 0.849$\times$ & [0.834, 0.865] & 25/31 \\
    Runtime (9)   & 0.829$\times$ & [0.801, 0.859] & 7/9   \\
    \bottomrule
  \end{tabular}
\end{table}

Table~\ref{tab:exec_summary} summarizes the gap. llvmbpf is faster on
21/31 benchmarks; the kernel wins on 10/31, primarily loop-dominated
workloads where simpler code has lower I-cache pressure. Code size tells
a cleaner story: llvmbpf is smaller on \emph{all} 31 benchmarks (geomean
0.496$\times$), confirming the gap is systematic.

\textbf{Root causes.} JIT-dump analysis of 22 benchmarks decomposes the
kernel's instruction surplus into three mechanisms covering 89\% of the
total: byte-load recomposition (50.7\%), absent conditional moves
(19.9\%), and fixed callee-saved registers (18.5\%).

\subsection{The Case Against Fixed Kernel Heuristics}
\label{sec:policy_sensitivity}

A fixed kernel heuristic would close the gap only if every optimization
were unconditionally profitable. We present two forms of evidence that
this assumption fails.

\textbf{Evidence 1: Policy sensitivity.}
Table~\ref{tab:cmov_ablation} shows an ablation study in llvmbpf where
\texttt{cmov} emission is toggled. Disabling \texttt{cmov}
\emph{hurts} programs with unpredictable branches
(\texttt{switch\_dispatch}: +26.3\%) but \emph{helps} programs with
predictable branches (\texttt{bounds\_ladder}: $-$18.1\%). The same
legal lowering helps one workload class and hurts another by comparable
magnitudes. We validate both directions in the kernel JIT via BpfReJIT: forcing
CMOV on predictable-branch \texttt{log2\_fold} degrades performance by
34.5\% (383.5$\to$590.0\,ns, $p{=}0.002$), while applying it to
unpredictable-branch \texttt{cmov\_select} yields a modest improvement
(744$\to$723\,ns, \S\ref{sec:eval_rejit}).

\begin{table}[t]
  \centering
  \caption{Cmov ablation in llvmbpf: profitability depends on workload.
  Validated in the kernel JIT via BpfReJIT re-JIT (\S\ref{sec:eval_rejit}).}
  \label{tab:cmov_ablation}
  \begin{tabular}{lrrr}
    \toprule
    Benchmark & Normal & No-cmov & $\Delta$ \\
    \midrule
    \texttt{switch\_dispatch}  & 213\,ns & 269\,ns & \textbf{+26.3\%} \\
    \texttt{binary\_search}    & 205\,ns & 229\,ns & \textbf{+11.7\%} \\
    \texttt{bounds\_ladder}    & 83\,ns  & 68\,ns  & $-18.1\%$ \\
    \texttt{large\_mixed\_500} & 415\,ns & 316\,ns & $-23.9\%$ \\
    \bottomrule
  \end{tabular}
\end{table}

\textbf{Why static analysis is insufficient.} Branch predictability
depends on \emph{runtime input distributions}, not just program
structure. A BPF program performing packet classification against a
hash table has data-dependent branches whose predictability varies with
traffic mix---a property that changes between deployments and over time.
No static analysis of BPF bytecode can determine the distribution of
live traffic at a particular deployment site.

\textbf{Evidence 2: Combination interference.}
Even if each optimization were individually safe, applying all of them
simultaneously can produce regressions. We built a ``fixed-all'' kernel
with all four optimizations hardcoded. While code-size effects compose
additively (each program's native code shrinks by exactly the sum of the
individual deltas), execution-time effects \emph{do not}.
Table~\ref{tab:fixed_preview} previews the key finding: the fixed-all
kernel regresses \texttt{log2\_fold} by 28.3\% and
\texttt{stride\_load\_16} by 14.2\%.\footnote{Table~\ref{tab:fixed_preview} and Table~\ref{tab:per_directive} report
results from two separate experimental environments (different VM
configurations and measurement days). The directional findings are
consistent (LEA hurts \texttt{stride\_load\_16}; CMOV hurts
\texttt{log2\_fold}), but absolute magnitudes differ due to
microarchitectural variability. We report both for transparency.}
The full per-directive isolation
analysis appears in \S\ref{sec:eval_fixed}.

\begin{table}[t]
  \centering
  \caption{Fixed-all kernel baseline: code size composes additively,
  execution time does not. Full isolation in Table~\ref{tab:per_directive}.}
  \label{tab:fixed_preview}
  \small
  \begin{tabular}{lrrr}
    \toprule
    Program & Exec $\Delta$ & Code $\Delta$ & Interpretation \\
    \midrule
    \texttt{rotate64\_hash}     & $-$16.8\% & $-$1{,}178\,B & Substrate win \\
    \texttt{pkt\_rss\_hash}     & $-$14.9\% & $-$151\,B  & Substrate win \\
    \texttt{load\_byte\_recomp} & $-$13.0\% & $-$12\,B   & Substrate win \\
    \texttt{stride\_load\_16}   & \textbf{+14.2\%} & $-$30\,B   & Combination regression \\
    \texttt{log2\_fold}         & \textbf{+28.3\%} & $-$2\,B    & CMOV regression \\
    \bottomrule
  \end{tabular}
\end{table}

The mechanism we need is not a better heuristic but a separation of
concerns: the kernel should enforce which native code variants are
\emph{safe to emit}, while the operator---who understands the
workload---specifies which safe variants to \emph{apply}, selectively
per program and per site.

%% ============================================================
\section{Design}
\label{sec:design}
%% ============================================================

\textsc{BpfReJIT} separates safety from optimization in the kernel JIT
by establishing a new kernel/userspace interface for post-load
specialization.  The kernel enforces which native code variants are safe
to emit for a given BPF pattern on the current CPU.  Privileged
userspace decides which safe variants to apply, based on workload
profile and deployment constraints.

\subsection{Architecture Overview}

Figure~\ref{fig:architecture} shows the two-plane architecture.
The interface is \texttt{BPF\_PROG\_JIT\_RECOMPILE}, a new BPF syscall
subcommand. Userspace submits a \emph{policy blob}---a compact binary
specification of per-site native instruction choices---via a sealed
memfd. The kernel validates and applies the blob, re-JITting the program
without re-verification.

\begin{figure}[t]
  \centering
  \small
  \begin{tabular}{|p{0.42\linewidth}|}
    \hline
    \textbf{Userspace Policy Plane} \\
    \hline
    Pattern scanning on xlated bytecode \\
    CPU + workload policy selection \\
    Selective per-site/per-family application \\
    Fleet-level A/B rollout \\
    Policy blob generation \\
    \hline
    \multicolumn{1}{c}{$\downarrow$ \texttt{BPF\_PROG\_JIT\_RECOMPILE}} \\
    \hline
    \textbf{Kernel Legality Plane} \\
    \hline
    Digest binding (prog\_tag SHA-256) \\
    Pattern matching + variable binding \\
    CPU feature gating (e.g., BMI2) \\
    Structural constraint validation \\
    Canonical-parameter extraction \\
    Parameterized arch-specific emitters \\
    Fail-closed fallback per rule \\
    \hline
  \end{tabular}
  \caption{Two-plane architecture of \textsc{BpfReJIT}. Userspace controls
    \emph{what} to optimize; the kernel controls \emph{how} safely.}
  \label{fig:architecture}
\end{figure}

\textbf{Core invariants.}
(I1)~The verified BPF bytecode (\texttt{xlated\_prog\_len}) is never
modified; policy affects only native code emission.
(I2)~No new side effects: the re-JIT'd code computes the same function.
(I3)~Fail-closed: if a rule's pattern match or constraint check fails,
that site falls back silently to stock JIT emission; a malformed policy
blob cannot crash or silently miscompile a program.

\textbf{Design alternatives considered.}
We considered three alternatives and rejected each:
(1)~\emph{Load-time hints}: hints at program load time cannot adapt to
post-deployment workload changes without program restart.
(2)~\emph{Kernel plugins/heuristics}: any fixed heuristic chosen by
kernel maintainers cannot accommodate deployment-specific workload
distributions (\S\ref{sec:policy_sensitivity}).
(3)~\emph{Native code upload}: allowing userspace to upload arbitrary
machine code would bypass all kernel safety guarantees and is
architecturally unacceptable.

\subsection{Worked Example: Conditional Select}
\label{sec:worked_example}

To make the mechanism/policy separation concrete, we trace a single
\textsc{Cond\_Select} optimization from policy request to native
emission.

\textbf{Stock behavior.} Consider a BPF ``select diamond'': a
conditional branch over two moves that assign different values to the
same register, followed by a merge. The stock JIT emits an x86
\texttt{cmp} + \texttt{jcc} + two \texttt{mov}s + a target label---five
instructions.

\textbf{Policy request.} The userspace scanner identifies this 4-instruction
diamond pattern starting at xlated instruction offset 42. It generates a
policy rule: \texttt{\{site\_offset=42, site\_len=4,
family=COND\_SELECT, choice=CMOVCC\}}.

\textbf{Kernel validation.} The kernel (1)~verifies the digest matches
the loaded program; (2)~checks that instructions 42--45 form a valid
diamond: straight-line after the branch, no interior edges from outside,
no helper calls or stores; (3)~binds variables: condition code, true
register, false register, destination; (4)~confirms x86 supports
\texttt{cmov} (always true on modern x86).

\textbf{Emission.} The emitter replaces the 5-instruction sequence with
\texttt{cmp} + \texttt{cmovcc}---two instructions. If any validation step
fails, the kernel silently falls back to stock emission.

\textbf{Policy sensitivity.} Whether this replacement is
\emph{profitable} depends on branch predictability: beneficial for
data-dependent conditions (hash lookups, packet classification),
harmful for monotone-threshold conditions where the branch predictor
achieves near-perfect accuracy. This decision requires workload context
that the kernel does not have.

\subsection{The BPF\_PROG\_JIT\_RECOMPILE Interface}

\begin{lstlisting}[language=C,caption=Core syscall interface.]
union bpf_attr {
    struct { /* BPF_PROG_JIT_RECOMPILE */
        __u32 prog_fd;    /* loaded program */
        __u32 policy_fd;  /* sealed memfd; 0=revert */
        __u32 flags;
        __u32 log_level;
        __aligned_u64 log_buf;
        __u32 log_size;
    } jit_recompile;
};
\end{lstlisting}

When \texttt{policy\_fd == 0}, the kernel reverts to stock JIT, giving
operators a one-call undo. The interface enables an iterative loop:
load $\to$ run $\to$ profile $\to$ generate policy $\to$ re-JIT $\to$
measure $\to$ refine---all without program restart or re-verification.

\subsection{Rule Families: Policy-Sensitive and Substrate}
\label{sec:families}

We define four rule families organized by profitability characteristics
(Table~\ref{tab:rule_families}).

\begin{table}[t]
  \centering
  \caption{Rule families in \textsc{BpfReJIT}. \textsc{Cond\_Select} is
  policy-sensitive; the other three are substrate optimizations that
  benefit from framework infrastructure.}
  \label{tab:rule_families}
  \small
  \begin{tabular}{llp{3.5cm}}
    \toprule
    Family & Type & Addresses \\
    \midrule
    \textsc{Cond\_Select} & Policy-sensitive & Absent cmov; profitability depends on branch predictability \\
    \textsc{Wide\_Mem}    & Substrate & Byte-load recomposition \\
    \textsc{Rotate}       & Substrate & Hash/checksum rotate idioms \\
    \textsc{Addr\_Calc}   & Substrate & Address computation fusion \\
    \bottomrule
  \end{tabular}
\end{table}

Each family defines: (1)~the BPF instruction pattern it matches,
(2)~the set of legal native variants, (3)~structural constraints
(straight-line, no side effects, no interior branch edges), and
(4)~CPU feature requirements (e.g., BMI2 for \texttt{rorx}).

\textbf{Why substrate families need the framework.}
One might argue that substrate families could simply be hardcoded as
unconditional kernel peepholes. Three observations argue against this.
First, \emph{update frequency}: the ROTATE family required three rounds
of pattern expansion (4-insn, 5-insn, 6-insn masked) as we discovered
new Clang emission patterns; updating a userspace descriptor takes 32
LOC, while each kernel pattern required ${\sim}$200 LOC.
Second, \emph{combination effects}: the per-directive isolation
experiment (\S\ref{sec:eval_fixed}) shows that LEA-only helps
\texttt{stride\_load\_4} ($-$11.9\%) but hurts \texttt{stride\_load\_16}
(+141.4\%), and fixed-all combines differently than the sum of parts.
Selective per-site application avoids these regressions.
Third, \emph{shared infrastructure}: all families share the same
validation pipeline, digest binding, policy blob format, and
fail-closed semantics---duplicating this per peephole would be
wasteful.

\subsection{Security Model and Trust Boundary}
\label{sec:security}

\textbf{Trusted computing base (TCB).}
The following components are trusted: the verified xlated bytecode, the
kernel's canonical-form emitters, CPU feature detection (\texttt{CPUID}),
and the \texttt{prog\_tag} digest computation.

\textbf{Untrusted input.} The policy blob content is untrusted. Every
field---site offset, rule kind, native choice, pattern descriptors---is
validated before use.

\textbf{Safety invariants.}
\begin{enumerate}
  \item \emph{Bytecode unchanged}: \texttt{xlated\_prog\_len} is identical
    before and after re-JIT; verified by comparing stored program length.
  \item \emph{No new side effects}: canonical emitters produce
    instruction sequences that compute the same function as the stock
    emission; they cannot introduce memory writes, helper calls, or
    new control flow.
  \item \emph{Bounded control-flow forms}: each canonical form has a
    fixed set of legal native instruction templates; the emitter
    selects from this set, not from arbitrary code.
  \item \emph{Fail-closed}: digest mismatch rejects the entire blob;
    individual rule failures fall back to stock emission.
\end{enumerate}

\textbf{Digest binding.} The policy blob carries \texttt{prog\_tag}
(SHA-256 of xlated bytecode). Tag mismatch rejects the entire blob.
The blob is passed via a sealed memfd (\texttt{F\_SEAL\_WRITE} +
\texttt{F\_SEAL\_SHRINK}), preventing TOCTOU attacks.

\textbf{CPU feature gating.} Each rule declares required CPU features;
the kernel checks CPUID before applying. A \texttt{rorx} request on a
CPU without BMI2 is silently rejected.

\textbf{Privilege.} \texttt{BPF\_PROG\_JIT\_RECOMPILE} requires
\texttt{CAP\_BPF}, the same privilege as \texttt{BPF\_PROG\_LOAD}.

\textbf{Known limitation: concurrent execution.} The current prototype
does not implement RCU-protected hot-swap of JIT images. Re-JIT should
be performed during a quiescent period (e.g., before attaching the
program to a hook). Full RCU protection is an engineering task, not a
design challenge: the kernel already supports atomic JIT image
replacement for \texttt{bpf\_prog\_realloc\_jit\_image()}.

\subsection{Declarative Pattern Extension}
\label{sec:v5}

A key question for any extensible framework is whether the kernel
component remains small and stable as the optimization catalog grows.
We address this through a \emph{declarative pattern extension}
mechanism.

\textbf{Problem.} The initial v4 design uses a closed \texttt{rule\_kind}
enum: each optimization has a hardcoded kernel validator. Adding ROTATE
support required 670 kernel LOC (validators for four pattern widths,
x86 emitters, CPU feature gating) plus 348 userspace LOC---1{,}018 LOC
total across 3 kernel files.

\textbf{Solution.} v5 moves pattern descriptions into the policy blob.
The kernel retains a small fixed set of \emph{canonical forms}
(e.g., \textsc{CF\_Rotate}, \textsc{CF\_Select}), each with a
parameterized emitter. A new pattern variant that maps to an existing
canonical form requires only a userspace descriptor edit---no kernel
changes. The pipeline is:

\begin{center}
\small
pattern descriptor $\to$ variable bindings $\to$ canonical parameters
$\to$ parameterized emitter
\end{center}

\textbf{Worked example.} When we discovered that Clang emits a 5-instruction
``two-copy'' rotate pattern (in addition to the original 4-instruction
pattern), we added support by writing a 32-LOC descriptor in the
userspace scanner. This descriptor specifies: (1)~5 BPF opcodes with
wildcard registers, (2)~3 constraints (shift amounts sum to 64, same
source register, same destination), and (3)~canonical bindings mapping
matched variables to \textsc{CF\_Rotate} parameters (source, destination,
shift amount, width). The kernel's existing rotate emitter handles the
rest. Zero kernel files were touched.

\textbf{Why this matters.} The kernel legality plane remains stable at
${\sim}$4 canonical forms even as the userspace pattern catalog grows.
This is the property that makes the framework maintainable: kernel
maintainers review and accept a small set of canonical emitters; pattern
variants are maintained by the optimization policy owner (e.g., the
Cilium team). Section~\ref{sec:eval_extensibility} quantifies the cost
reduction.

%% ============================================================
\section{Implementation}
\label{sec:implementation}
%% ============================================================

\textsc{BpfReJIT} modifies the Linux kernel (based on v7.0-rc2) in
approximately 1{,}800 LOC across 7 files, plus a userspace
scanner/blob-builder (${\sim}$1{,}200 LOC).

\textbf{Kernel components.}
(1)~\texttt{BPF\_PROG\_JIT\_RECOMPILE} plumbing and policy blob parsing
(${\sim}$350 LOC); (2)~a generic per-rule validator checking structural
constraints, pattern matching, and CPU features (${\sim}$150 LOC);
(3)~four canonical-form validators and x86 emitters (${\sim}$640 LOC);
(4)~rule dispatch in the JIT main loop (${\sim}$120 LOC);
(5)~re-JIT image installation (${\sim}$80 LOC).

\textbf{Rule dispatch.} We instrument \texttt{do\_jit()} to check for
applicable rules before each BPF instruction:

\begin{lstlisting}[language=C,caption=Rule dispatch in do\_jit().]
for (i = 1; i <= insn_cnt; i++, insn++) {
    rule = bpf_jit_lookup_rule(ruleset, i-1);
    if (rule) {
        int len = bpf_jit_emit_rule_x86(
            prog, &ctx, rule, addrs, i-1);
        if (len >= 0) {
            i    += rule->site_len - 1;
            insn += rule->site_len - 1;
            continue;
        }
        /* fallback to stock emission */
    }
    /* stock switch-case ... */
}
\end{lstlisting}

Rule lookup is O($\log n$) via sorted-array binary search on site offset;
with typical rule counts under 200, lookup completes in under 8 comparisons.
Failed emission falls through to stock processing without side effects.

\textbf{Validation pipeline.} Each rule passes through four layers:
(1)~structural (bounds, subprogram containment, known canonical form,
CPU features); (2)~pattern (straight-line, no helpers/stores/atomics,
opcode matching, variable binding); (3)~canonical-parameter extraction
(binding table maps matched variables to emitter parameters);
(4)~form-specific checks (e.g., ROTATE verifies shift amounts sum to
operand width).

%% ============================================================
\section{Evaluation}
\label{sec:evaluation}
%% ============================================================

We evaluate \textsc{BpfReJIT} along four axes: (1)~whether a fixed
kernel baseline suffices (it does not), (2)~effectiveness of selective
re-JIT, (3)~compatibility and safety on production programs, and
(4)~extensibility cost.

\textbf{Setup.} Microbenchmark re-JIT experiments use a rigorous
configuration: 5 warmups, 10 measured iterations, 1{,}000 repeats per
iteration, single guest vCPU pinned to host CPU~23, host governor
\texttt{performance}, turbo disabled. The guest runs our modified
kernel~7.0-rc2 inside QEMU/KVM. We report median \texttt{exec\_ns} and
paired Wilcoxon signed-rank $p$-values with BH correction.

\subsection{RQ1: Can a Fixed Kernel Heuristic Close the Gap?}
\label{sec:eval_fixed}

To test whether \textsc{BpfReJIT}'s policy plane is necessary, we built
six kernel variants from a common source tree: \texttt{stock} (no
optimizations), four single-directive builds
(\texttt{CMOV-only}, \texttt{ROTATE-only}, \texttt{WIDE-only},
\texttt{LEA-only}), and \texttt{fixed-all} (all four unconditionally
enabled). Each was tested on six benchmark programs across three
same-day repetitions; we report the median of three runs.

\begin{table*}[t]
  \centering
  \caption{Per-directive isolation: execution-time delta vs.\ same-day stock.
  Code-size effects compose additively; execution-time effects do not.
  CMOV-only changes codegen for \texttt{log2\_fold} only and hurts it.
  LEA-only helps \texttt{stride\_load\_4} but hurts \texttt{stride\_load\_16}.
  Fixed-all combines all regressions.}
  \label{tab:per_directive}
  \small
  \begin{tabular}{lrrrrrr}
    \toprule
    Program & Stock (ns) & ROTATE-only & WIDE-only & LEA-only & CMOV-only & fixed-all \\
    \midrule
    \texttt{rotate64\_hash}      & 307 & $-$12.1\%  & $-$0.3\%  & +60.6\%\rlap{$^\dagger$} & +16.9\%\rlap{$^\dagger$} & $-$52.8\% \\
    \texttt{pkt\_rss\_hash}      & 183 & +2.7\%     & $-$3.3\%  & $-$15.3\%  & +20.8\%\rlap{$^\dagger$} & +0.5\%    \\
    \texttt{load\_byte\_recomp}  & 487 & +2.9\%\rlap{$^\dagger$} & \textbf{$-$14.2\%} & +3.9\%\rlap{$^\dagger$}  & $-$7.6\%\rlap{$^\dagger$} & +9.0\% \\
    \texttt{stride\_load\_4}     & 616 & +5.8\%\rlap{$^\dagger$} & +2.3\%   & \textbf{$-$11.9\%} & $-$0.5\%\rlap{$^\dagger$} & $-$10.7\% \\
    \texttt{stride\_load\_16}    & 261 & +131.4\%\rlap{$^\dagger$}& +14.9\% & \textbf{+141.4\%}  & +119.9\%\rlap{$^\dagger$} & +110.7\% \\
    \texttt{log2\_fold}          & 948 & +2.0\%\rlap{$^\dagger$} & $-$2.3\% & +19.1\%\rlap{$^\dagger$} & \textbf{+19.7\%} & +10.4\% \\
    \bottomrule
    \multicolumn{7}{l}{\footnotesize Bold = directive changed codegen for that program.
    $\dagger$ = codegen unchanged; delta is measurement noise.} \\
    \multicolumn{7}{l}{\footnotesize \texttt{stride\_load\_16} shows large $\dagger$ deltas across all builds (119--131\%), indicating a} \\
    \multicolumn{7}{l}{\footnotesize systematic timing artifact (likely thermal/frequency drift between same-day VM boots).}
  \end{tabular}
\end{table*}

Table~\ref{tab:per_directive} presents the per-directive isolation
results. Three findings emerge.

\textbf{Finding 1: CMOV is policy-sensitive.}
\texttt{CMOV-only} changes native code for exactly one program
(\texttt{log2\_fold}: 648$\to$682 bytes) and degrades it by 19.7\%.
The other five programs retain identical \texttt{jited\_prog\_len},
confirming that their timing deltas under CMOV-only are noise.

\textbf{Finding 2: LEA has program-dependent profitability.}
\texttt{LEA-only} changes native code for both stride benchmarks
(517$\to$511 bytes). It helps \texttt{stride\_load\_4} ($-$11.9\%) but
\emph{hurts} \texttt{stride\_load\_16} (+141.4\%) despite reducing code
size by the same amount. The regression likely stems from instruction
alignment or decode-pipeline effects that differ between the two access
patterns.

\textbf{Finding 3: Combination effects are non-additive.}
The \texttt{fixed-all} build produces code sizes that are the exact sum
of individual deltas, but execution times diverge sharply. For
\texttt{rotate64\_hash}, fixed-all is $-$52.8\% (much better than
individual isolations suggest); for \texttt{stride\_load\_16}, fixed-all
is +110.7\% (the LEA regression persists and compounds).

\textbf{Takeaway.} A fixed kernel heuristic that unconditionally applies
all four optimizations would degrade 2 of 6 tested programs. Selective
per-site application---the capability \textsc{BpfReJIT} provides---avoids
these regressions while capturing the gains.

\subsection{RQ2: How Effective Is Selective Re-JIT?}
\label{sec:eval_rejit}

Table~\ref{tab:per_family} presents per-family results under
\textsc{BpfReJIT}'s selective policy (10$\times$1000 pinned configuration).

\begin{table*}[t]
  \centering
  \caption{Per-family re-JIT results under selective policy
  (rigorous pinned 10$\times$1000 configuration).
  Speedup = stock median / re-JIT median; values $<$1 indicate policy hurts.}
  \label{tab:per_family}
  \small
  \begin{tabular}{llrrrrrl}
    \toprule
    Policy & Benchmark & Stock (ns) & Re-JIT (ns) & Speedup & Code $\Delta$ & $p$ & Interpretation \\
    \midrule
    \textsc{Rotate}+\textsc{Wide} & \texttt{rotate64\_hash} & 68.0  & 57.0  & 1.193$\times$ & $-$35.0\% & 0.002 & Combined optimization \\
    \textsc{Rotate}        & \texttt{pkt\_rss\_hash}   & 21.0  & 17.0  & 1.235$\times$ & $-$15.3\% & 0.002 & Pure rotate gain \\
    \textsc{Addr\_Calc}    & \texttt{stride\_load\_16} & 293.0 & 281.0 & 1.052$\times$ & $-$1.2\%  & 0.012 & Modest but significant \\
    \textsc{Wide\_Mem}     & \texttt{load\_byte\_recomp} & 223.0 & 226.0 & 0.978$\times$ & $-$2.8\% & 0.164 & Code-size win only \\
    \textsc{Cond\_Select}  & \texttt{log2\_fold}       & 383.5 & 590.0 & 0.655$\times$ & +5.3\% & 0.002 & Policy-sensitivity demo \\
    \bottomrule
  \end{tabular}
\end{table*}

\textbf{ROTATE} delivers the strongest gains: \texttt{pkt\_rss\_hash}
improves from 21.0\,ns to 17.0\,ns (1.235$\times$, $p{=}0.002$) with
15.3\% code reduction; \texttt{rotate64\_hash} under combined
ROTATE+WIDE policy improves 1.193$\times$ with 35.0\% code reduction.

\textbf{ADDR\_CALC illustrates the core thesis.}
On \texttt{stride\_load\_16}, the LEA-only kernel-fixed baseline
\emph{regresses} by 141\% (Table~\ref{tab:per_directive}),
while \textsc{BpfReJIT}'s selective application \emph{improves}
performance by 5.2\% ($p{=}0.012$). Both apply the same legal
transformation; the only difference is \emph{where}: \textsc{BpfReJIT}
applies LEA only at sites the userspace scanner identifies as
profitable, whereas the kernel-fixed baseline applies it at every
eligible site. Unconditional application turns a win into a 2.4$\times$
regression; selective policy avoids it.

\textbf{WIDE\_MEM} shows code-size reduction ($-$2.8\%) but the runtime
difference is not statistically significant ($p{=}0.164$). We report
this honestly as a limitation.

\textbf{COND\_SELECT} demonstrates bidirectional policy sensitivity
in the kernel JIT. On predictable-branch \texttt{log2\_fold}, forcing
CMOV produces a 34.5\% regression ($p{=}0.002$). On
unpredictable-branch \texttt{cmov\_select}, applying CMOV yields a
modest 2.8\% improvement (744$\to$723\,ns median, $n{=}10$), consistent
with the 5.5$\times$ benefit observed in the llvmbpf reference
(Table~\ref{tab:cmov_ablation}). The kernel-side benefit is smaller
because the kernel JIT already partially optimizes the conditional
sequence; the key evidence is the \emph{sign reversal}: the same
transformation helps one workload and hurts another.

\textbf{Takeaway.} Selective re-JIT achieves statistically significant
speedups for ROTATE (1.24$\times$) while avoiding the regressions that
the fixed-all kernel baseline incurs.

\subsection{RQ3: Is the Framework Safe and Compatible?}
\label{sec:eval_safety}

We validate safety through structural properties and production
compatibility.

\textbf{Bytecode invariant.} Re-JIT preserves verified bytecode exactly.
For every re-JIT'd program, \texttt{xlated\_prog\_len} is identical
before and after. For example, \texttt{log2\_fold} remains 1{,}112 bytes
while JIT output changes from 648 to 682; \texttt{rotate64\_hash}
remains 7{,}984 while JIT bytes shrink from 3{,}559 to 2{,}313.

\textbf{Result correctness.} All 12 kernel-fixed-baseline runs and all
re-JIT experiments return the same observable program output as stock.
For example, \texttt{log2\_fold} returns 9 under stock, CMOV, and
fixed-all; \texttt{rotate64\_hash} returns the same 64-bit hash under
all configurations.

\textbf{Production corpus.} We test compatibility on production BPF
programs from Calico (8 objects, 61 programs) and Suricata (1 program):
\begin{itemize}
  \item 60 baseline compiles succeed. \textbf{60/60 v5 recompiles
    succeed} with zero syscall failures.
  \item 45 programs have optimization sites applied (197 CMOV + 108
    WIDE + 10 ROTATE sites across the corpus).
  \item Code-size geomean ratio: 1.001$\times$ (negligible overall
    change); largest reduction: \texttt{calico\_tc\_maglev} at $-$4.4\%
    (10 ROTATE sites).
\end{itemize}

Note: loxilb objects (18 programs) fail to load due to non-standard ELF
section names that libbpf rejects. Cilium objects (the highest-value
target, with 408 CMOV sites in \texttt{bpf\_xdp.bpf.o} alone) fail at
\texttt{bpf\_object\_\_open\_file()} because they require Cilium's
custom BTF generation and runtime map pinning infrastructure.
Both failures are libbpf environment issues, not \textsc{BpfReJIT}
limitations; we expect them to be resolvable with dedicated per-project
loading shims. End-to-end throughput evaluation on a production
deployment is future work.

\textbf{Zero overhead.} Programs with no matching policy incur no
overhead: rule lookup returns null immediately, and programs that never
receive a recompile call follow the identical code path as stock JIT.

\textbf{Takeaway.} \textsc{BpfReJIT} preserves bytecode invariant,
maintains result correctness, and achieves 100\% recompile success on
60 production programs. The framework validates compatibility and
safety; end-to-end deployment evaluation with throughput measurement
remains future work.

\subsection{RQ4: How Extensible Is the Framework?}
\label{sec:eval_extensibility}

Table~\ref{tab:extensibility} quantifies extension cost across three
scenarios.

\begin{table}[t]
  \centering
  \caption{Extension cost: v4 closed-enum vs.\ v5 declarative patterns.}
  \label{tab:extensibility}
  \small
  \begin{tabular}{lrrrr}
    \toprule
    Scenario & Kernel & Userspace & Total & Kernel files \\
    \midrule
    v4: add ROTATE          & 670 & 348 & 1{,}018 & 3 \\
    v4: add WIDE\_MEM       & 179 & 98  & 277     & 3 \\
    v5: new variant, same form & 0 & 32 & 32      & 0 \\
    v5: new canonical form  & 111 & 55  & 166     & 3 \\
    \bottomrule
  \end{tabular}
\end{table}

Under v4, adding ROTATE required 670 kernel LOC (validators for four
pattern widths plus x86 emitters) and 348 userspace LOC across 3 kernel
files.

Under v5, adding a new ROTATE \emph{variant} that maps to the existing
\textsc{CF\_Rotate} canonical form requires \textbf{0 kernel LOC} and
\textbf{32 userspace LOC}---a single pattern descriptor. Even a new
canonical form costs only 166 LOC because the validation pipeline is
shared.

\textbf{Connection to thesis.} The 31.8$\times$ cost reduction
(1{,}018 $\to$ 32 LOC for same-form variants) demonstrates that the
kernel legality plane can remain stable at ${\sim}$4 canonical forms
while the userspace pattern catalog grows with new compiler emission
patterns, new CPU variants, and new workload-specific heuristics. This
is the property that makes mechanism/policy separation maintainable in
practice.

\textbf{Takeaway.} Declarative patterns reduce same-form extension cost
by 31.8$\times$ with zero kernel files touched, keeping the kernel
component small and stable.

\subsection{Cross-Domain Directive Coverage}
\label{sec:eval_census}

To assess generality beyond networking, we scanned all 514 compiled BPF
objects in our corpus across five program domains.

\begin{table}[t]
  \centering
  \caption{Cross-domain directive site census (514 objects, 444{,}610 insns).
  CMOV appears in all four non-trivial domains.}
  \label{tab:cross_domain}
  \small
  \begin{tabular}{lrrrrrr}
    \toprule
    Domain & Objs & CMOV & WIDE & ROT & Total & w/ Sites \\
    \midrule
    Networking  & 61  & 1{,}051 & 1{,}864 & 30    & 2{,}945 & 39 (64\%) \\
    Tracing     & 57  & 109     & 0       & 0     & 109     & 20 (35\%) \\
    Security    & 6   & 3       & 0       & 0     & 3       & 2 (33\%)  \\
    Testing     & 361 & 74      & 6       & 1{,}810 & 1{,}890 & 37 (10\%) \\
    Examples    & 29  & 0       & 0       & 0     & 0       & 0 (0\%)   \\
    \midrule
    \textbf{Total} & \textbf{514} & \textbf{1{,}237} & \textbf{1{,}870} & \textbf{1{,}840} & \textbf{4{,}947} & \textbf{98 (19\%)} \\
    \bottomrule
  \end{tabular}
\end{table}

CMOV is the most cross-cutting family, appearing in networking (Cilium,
Calico, Katran), tracing (20 of 57 BCC tools including \texttt{biostacks},
\texttt{cpudist}, \texttt{runqlat}, programs using histogram binning
patterns), and security (systemd LSM/cgroup programs). WIDE and ROTATE
are concentrated in networking and testing respectively.
ADDR\_CALC (LEA) sites are absent from the census because the
multi-instruction address computation pattern requires post-verifier
context that the bytecode-level scanner does not currently detect;
LEA sites are identified only during JIT lowering.

\textbf{Takeaway.} Directive sites are not limited to networking: 35\%
of production tracing tools contain CMOV candidates. The policy-sensitive
family that motivates mechanism/policy separation is present across BPF
program domains.

%% ============================================================
\section{Discussion}
\label{sec:discussion}
%% ============================================================

\textbf{Two categories of evidence.}
Our evidence for mechanism/policy separation comes in two forms.
\textsc{Cond\_Select} provides the strongest policy-sensitivity
evidence: the same legal optimization produces a 34.5\% degradation or
a 5.5$\times$ improvement depending on branch predictability, and branch
predictability depends on runtime input distributions that the kernel
cannot observe. The other three families are substrate optimizations
where the framework's value lies in selective composition, rapid
update, and shared infrastructure. We are transparent that only CMOV
currently demonstrates clear bidirectional policy sensitivity.

\textbf{Scope of claims.} Our results are from a single x86
microarchitecture (Intel Arrow Lake-S). We conjecture that policy
sensitivity increases on architectures with different branch predictor
designs (e.g., ARM64's \texttt{csel}), but we have not validated this.
The per-directive isolation experiment uses six benchmarks chosen for
directive coverage; a broader program set may reveal additional
interaction effects.

\textbf{LLVM as upper bound.} llvmbpf serves as an upper bound reference,
not a direct competitor. Running LLVM -O3 in the kernel is impractical;
\textsc{BpfReJIT} captures a portion of the available headroom in a
kernel-compatible way.

\textbf{Complementarity with bytecode optimizers.} K2, Merlin, and EPSO
optimize BPF bytecode \emph{before} JIT; \textsc{BpfReJIT} optimizes
native code \emph{after}. A deployment could use both layers without
interference.

\textbf{Limitations.}
(1)~\textsc{Wide\_Mem} does not show a statistically significant latency
win ($p{=}0.164$), though it reduces code size.
(2)~Cilium and loxilb programs fail to load in our test environment due
to BTF/section compatibility issues unrelated to \textsc{BpfReJIT}.
(3)~The re-JIT installation path is not yet RCU-protected for
concurrent execution; re-JIT should occur before program attachment.
(4)~End-to-end deployment evaluation with throughput measurement is
future work; the 60/60 result validates compatibility, not performance
impact on production workloads.

%% ============================================================
\section{Related Work}
\label{sec:related}
%% ============================================================

\textbf{BPF-level optimization.}
K2~\cite{k2} applies stochastic superoptimization to BPF bytecode.
Merlin~\cite{merlin} lifts BPF to LLVM IR for optimization.
EPSO~\cite{epso} uses evolutionary synthesis at the bytecode level.
All three operate above the JIT and cannot influence native instruction
selection. \textsc{BpfReJIT} operates at the JIT backend, supports
post-load re-optimization without re-verification, and enables per-site
selective application. The systems are complementary.

\textbf{Superoptimization.}
Massalin's superoptimizer~\cite{superoptimizer} and
STOKE~\cite{stoke} find optimal native sequences.
Bansal and Aiken~\cite{credal} automate peephole rule generation.
Our problem is not finding better sequences but deciding which
\emph{known-legal variant} to emit for a given workload.

\textbf{Feedback-directed and adaptive JIT compilation.}
Profile-guided optimization~\cite{feedback_directed} and adaptive JIT
techniques~\cite{jit_survey} (e.g., HotSpot, V8, Graal) use runtime
feedback to guide compilation. These systems have full control over
their compiler backend. \textsc{BpfReJIT} applies the same principle to
a constrained setting: the kernel BPF JIT, where the compiler is part of
the kernel and cannot be replaced, but can be steered through a safe
interface.

\textbf{Auto-tuning frameworks.}
Halide~\cite{halide} separates algorithm from schedule; TVM and XLA
auto-tune compilation parameters for deep learning workloads. Our
mechanism/policy separation borrows the principle of externalizing
optimization decisions, but operates at a much narrower scope (per-site
instruction selection) with much stronger safety constraints (kernel
TCB, no arbitrary code).

\textbf{Compiler backend design.}
LLVM's TableGen-based instruction selection~\cite{llvm} describes
target-specific lowering patterns. Our canonical forms are a
safety-restricted subset of instruction selection, constrained to
pre-verified equivalence-preserving lowerings.

\textbf{Kernel live patching.}
Linux live patching (kpatch, livepatch) modifies running kernel code,
but operates at function granularity and requires source-level changes.
\textsc{BpfReJIT} modifies JIT output at instruction granularity for
already-verified BPF programs, with a different safety model
(bytecode-invariant, fail-closed).

%% ============================================================
\section{Conclusion}
\label{sec:conclusion}
%% ============================================================

We characterized the performance gap between the Linux kernel eBPF JIT
and LLVM~-O3: a 15\% execution-time gap and 2$\times$ code-size gap
rooted in three backend lowering deficiencies. We showed that these
deficiencies cannot be fully addressed by fixed kernel heuristics: CMOV
is policy-sensitive (34.5\% degradation on predictable branches,
$p{=}0.002$), and a fixed-all baseline produces combination regressions
on 2 of 6 tested programs.

\textsc{BpfReJIT} separates mechanism (kernel safety) from policy
(userspace profitability) via \texttt{BPF\_PROG\_JIT\_RECOMPILE}. Four
rule families cover the identified gaps, with selective application
avoiding the regressions that fixed heuristics cannot. Evaluation shows
ROTATE achieves 1.24$\times$ speedup ($p{=}0.002$), 60/60 production
programs recompile successfully, and declarative patterns reduce
extension cost by 31.8$\times$.

When profitability depends on deployment context---runtime data
distributions, workload mix, microarchitecture---backend optimization
policy should be externalized from the kernel. \textsc{BpfReJIT}
demonstrates that this externalization is feasible, safe, and
practical.

\begin{acks}
Anonymized for submission.
\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\appendix

\section{Benchmark Descriptions}
\label{appendix:benchmarks}

\begin{table}[h]
  \centering
  \caption{Key benchmark descriptions.}
  \label{tab:bench_desc}
  \small
  \begin{tabular}{llp{4.2cm}}
    \toprule
    Benchmark & Category & Description \\
    \midrule
    \texttt{log2\_fold}            & ALU       & Integer log2 with predictable branches; CMOV policy-sensitivity case \\
    \texttt{switch\_dispatch}      & ctrl-flow & Multi-way dispatch with unpredictable branches; CMOV benefit case \\
    \texttt{rotate64\_hash}        & ALU       & 64-bit rotate hash; 115 rotate sites \\
    \texttt{pkt\_rss\_hash}        & hash      & RSS hash computation; 11 rotate sites \\
    \texttt{load\_byte\_recompose} & memory    & 8-byte recompose from byte loads \\
    \texttt{stride\_load\_4}       & memory    & 4-byte strided loads; LEA candidate \\
    \texttt{stride\_load\_16}      & memory    & 16-byte strided loads; LEA regression case \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Policy Blob Binary Format}
\label{appendix:blob}

The policy blob is a flat binary structure:
(1)~\texttt{bpf\_jit\_policy\_hdr} (32 bytes) containing magic, version,
rule count, program instruction count, \texttt{prog\_tag} digest, and
architecture ID;
(2)~array of \texttt{bpf\_jit\_rewrite\_rule} (variable-length in v5)
each specifying site offset, site length, canonical form, native choice,
CPU feature requirements, and (in v5) inline pattern descriptors with
constraint arrays and canonical binding tables;
(3)~rule-specific payload data referenced by offset/length fields.

The blob is sealed via \texttt{F\_SEAL\_WRITE} and
\texttt{F\_SEAL\_SHRINK} before submission, preventing TOCTOU
modification between digest validation and rule application.

\section{Production Corpus Details}
\label{appendix:corpus}

\begin{table}[h]
  \centering
  \caption{Directive site census across production corpus.}
  \label{tab:census}
  \small
  \begin{tabular}{lrrrrr}
    \toprule
    Project & Progs & CMOV & WIDE & ROTATE & Total \\
    \midrule
    Calico    & 60 & 196 & 108   & 10 & 314  \\
    Suricata  & 1  & 1   & 0     & 0  & 1    \\
    \midrule
    \textbf{Tested} & \textbf{61} & \textbf{197} & \textbf{108} & \textbf{10} & \textbf{315} \\
    \midrule
    \multicolumn{6}{l}{\textit{Inventory-only (load failures):}} \\
    loxilb    & 18 & 98  & 1{,}729 & 0  & 1{,}827\\
    \bottomrule
  \end{tabular}
\end{table}

Calico programs loaded and recompiled successfully (60/60).
loxilb objects failed at \texttt{bpf\_object\_\_load()} due to
non-standard ELF section names; site counts are from scanner inventory
only, not validated via recompile.

\section{Interaction Effects: Code Size vs.\ Execution Time}
\label{appendix:interaction}

\begin{table}[h]
  \centering
  \caption{Code-size composition is exactly additive; execution-time
  composition is not. $\sum$individual = sum of per-directive deltas.}
  \label{tab:interaction}
  \small
  \begin{tabular}{lrrrr}
    \toprule
    Program & fixed-all & $\sum$individual & fixed-all & $\sum$individual \\
            & exec $\Delta$ & exec $\Delta$ & code $\Delta$ & code $\Delta$ \\
    \midrule
    \texttt{rotate64\_hash}  & $-$162\,ns & +200\,ns & $-$1178 & $-$1178 \\
    \texttt{pkt\_rss\_hash}  & +1\,ns     & +9\,ns   & $-$151  & $-$151  \\
    \texttt{load\_byte\_rec} & +44\,ns    & $-$73\,ns & $-$12  & $-$12   \\
    \texttt{stride\_load\_4} & $-$66\,ns  & $-$26\,ns & $-$30  & $-$30   \\
    \texttt{stride\_load\_16}& +289\,ns   & +1064\,ns & $-$30  & $-$30   \\
    \texttt{log2\_fold}      & +99\,ns    & +365\,ns  & $-$2   & $-$2    \\
    \bottomrule
  \end{tabular}
\end{table}

\end{document}
